### 2018-03-16 paper.Rmd
added details on versioning scheme

We chose to treat participants separate from the above hierarchy because children can occur across transcripts (e.g., the Brown Corpus). A participant is associated with every word and utterance, including a name, role, 3-letter CHILDES identifier (CHI, MOT, FAT, etc.), and the range of ages (or age of corresponding child) for which they are observed. For non-child participants, the record contains an identifier for the target child to associate caregivers and children.
Technical Implementation

@@

>>>>

We chose to treat participants separate from the above hierarchy because children can occur across transcripts (e.g., the Brown Corpus). A participant is associated with every word and utterance, including a name, role, 3-letter CHILDES identifier (CHI, MOT, FAT, etc.), and the range of ages (or age of corresponding child) for which they are observed. For non-child participants, the record contains an identifier for the target child to associate caregivers and children.

Technical Implementation

@@

[[Details of extraction]]
[[Details of testing: Why trust our parse over your in-house library?]]

Versioning

To reflect changes in the CHILDES database as new corpora are added or previous annotations revised, we produce a new versioned parse of the complete database every [[n]] months. By default, users connect to the most recent version. To support reproduction of results with previous versions of the database, we provide hosted versions of the last [[m]] versions so that researchers can refer to specific releases. Compressed .sql files are available for download for [[r]] years.
